---
title: "Lab 03 - Nobel laureates"
author: "Jessie"
date: "1/24"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1
Observations: 935, variables: 26, each row represents an observation.

```{r ex1}
glimpse(nobel)
```
### Exercise 2
```{r ex2}
nobel_living<-nobel
nobel_living<- nobel_living %>% filter( !is.na(country), gender!="org", is.na(died_date)) 
```

### Exercise 3
According to the bar plot, the title is true for economics and medicine. But still over half of the noble prize owners are based in the U.S. in the field of chemistry and physics.
```{r ex3}
nobel_living <- nobel_living %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )
nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
ggplot(nobel_living_science, aes(x=country_us, fill=category)) + 
  geom_bar() +
  facet_wrap(~category, nrow=4)

```
### Exercise 4
105 laureates were born in the U.S.
```{r ex4}
nobel_living <- nobel_living %>%
  mutate(
    born_country_us = if_else(born_country == "USA", "USA", "Other")
  )
nobel_born_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
glimpse(nobel_born_science)
sum(nobel_born_science$born_country_us %in% c ("USA"))
```

### Exercise 5

It seems that the majority of U.S. laureates are also born in the U.S. in all subjects. But there is a certain amount of people who are not born in the U.S. but has bases in the U.S. The title seems true.
```{r ex5}
nobel_living_science <- nobel_living_science %>%
  mutate(
    born_country_us = if_else(born_country == "USA", "USA", "Other")
  )
nobel_born_science <- nobel_living_science %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
ggplot(nobel_born_science, aes(x=country_us, fill=born_country_us)) + 
  geom_bar() +
  facet_wrap(~category, nrow=4)
```

### Exercise 6
Germany and United Kingdom
...
```{r ex6}
nobel_born_science %>% 
  filter(country_us == "USA") %>%
  filter(born_country_us !="USA") %>%
  count(born_country) %>%
  arrange(desc(n))
```
